Using Fundamental Measure Theory to treat the two-point pair distribution function of the Inhomogeneous Hard-Sphere Fluid

### 2013-06-19 papers/pair-correlation/paper.tex
cut bad text from tex and clean up diagram examples Tested everything on node37.
updated pair-dist paper.tex with an outline of sections and updated plot-ghs.py with a leastsq function that jeffs version of python has Tested everything on node09.

%\maketitle

@@

>>>>>>> Stashed changes

>>>>

\section{Why does pair distribution matter?}
\subsection{Interfaces are important}
\subsection{cDFT theory enables treatment of inhomogeneous systems}
\subsection{Pair distribution function is key input in thermodynamic perturbation theory}
The pair distribution function is a key input into thermodynamic
perturbation theory, which is widely used for treating dispersion
interactions in fluids.  In most cases, the hard-sphere fluid is used
as the reference system, making the pair distribution function of the
hard-sphere system an important quantity.
\subsection{Explain what the $a_1$ in thermodynamic perturbation theory is}

\section{What has been done before?}
\subsection{Gloor simple method, problematic}
\subsection{Fischer accurate but slow}

\section{Triplet correlation function?}

\section{What is our new idea?}

\section{What does it look like (graphs that show the function itself)?}
\subsection{Fit to radial distribution function}
%% Figure~\ref{fig:radial-distribution} shows...
%% \begin{figure}
%%   \Huge{Need figure here}
%%   \caption{Plot of the radial distribution function, with our fit.}\label{fig:radial-distribution}
%% \end{figure}
%% \subsection{Pair distribution function}
%% Figure~\ref{fig:pair-distribution} shows...
%% \begin{figure}
%%   \Huge{Need figure here}
%%   \caption{Plot of the pair distribution function near a hard wall.
%%     How do we plot this?}\label{fig:pair-distribution}
%% \end{figure}

%% \section{How well does it work?}
%% Figure~\ref{fig:dadz} shows...
%% \begin{figure}
%%   \includegraphics[width=5cm]{figs/dadz}
%%   \caption{Plot of $\frac{da_1}{dz}$ near a hard
%%     wall. For what $\Phi$?}\label{fig:dadz}
%% \end{figure}

\section{THE END OF THE PAPER}

@@
